---
title: "CodeBook"
author: "Sundar"
date: "Sunday, April 26, 2015"
output: html_document
---
This is the code boox explaining the "Final_Result.txt" file, which is constructed 
as per the instructions given in the assignment page. I will discuss in detail, 
how this data file was constructed.

You can look at the data using the following commands
```{r}
Result <- read.table("Final_Result.txt")
View(Result)
```
The variables in the files are as follows
```{r, echo=FALSE}
load("test.RData")
Column_Names
```

The above mentioned variables are taken from the "Features.txt" file from the 
original data source.

These variables were used to estimate variables of the feature vector for each pattern:  
'-XYZ' is used to denote 3-axial signals in the X, Y and Z directions.

tBodyAcc-XYZ, 
tGravityAcc-XYZ, 
tBodyAccJerk-XYZ, 
tBodyGyro-XYZ, 
tBodyGyroJerk-XYZ,  
tBodyAccMag, 
tGravityAccMag, 
tBodyAccJerkMag, 
tBodyGyroMag, 
tBodyGyroJerkMag, 
fBodyAcc-XYZ, 
fBodyAccJerk-XYZ, 
fBodyGyro-XYZ, 
fBodyAccMag, 
fBodyAccJerkMag, 
fBodyGyroMag, 
fBodyGyroJerkMag, 

The set of variables that were estimated (and of our interest) from these signals are: 

mean(): Mean value
std(): Standard deviation

# Algorithm Used

#### Section 1. 
Reading the details of activity labels and feature labels  
This is common for both test and training datasets. Above mentioned data are read
from activity_labels.txt and features.txt files

#### Section 2. 
Extract the features corresponding to mean and standard deviation. I used
"Grep" functionality to extract this features. 

I used "mean" and "std" as tokens to extract relevant features and their index.
Using this index at alater point I will extract only colums of interest form 
"X_..." file.
eg) Mean_Features <- grep("mean",as.character(Feature_Labels$V2),ignore.case = FALSE)

#### Section 3. Read the Activity and the Subject data from test and train data
I read the subject id and the activity id from the test and the training folders
from subject_.. and y_... files respectively


#### Section 4. Read, extract and rename relavent columns from test and training files
Using the Column index calculated in section 2, I extract the relevant columns 
from X_... files in test and train folder.
Once extracting the relavent columns, I rename them using the column names calculated 
in section 2.


#### Section 5. Add the activity type and the subject Id columns to test and train datasets
The subject Id and the activity Id extracted in section 3 is appended to test and
training set appropriately. I read the training subject id and the activity from
training folder. This gets added as a column to the training dataframe. Same approach
is used for test dataframe.

#### Section 6. Merge the Dataframes
I rbind the test and the training data frames to form a complete dataframe

#### Section 7. Change the activity column to a factor with appropriate lables
I assigned the activity labels to the Activity_Id column, this was extracted in 
section 1

#### Section 8. Calculate means for all columns grouped by subject ID and activity ID
Finally, I use the "group_by" operation to group the merged data bythe subject_id and 
the activity_id. this data is then used as an input to "summarise_each" function 
to calculate the mean of all columns but grouped by subject and activity id.

